working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-03-03 Manuscript_draft/Manuscript_draft.Rmd
small edit
edits

@@

Results of hand cross-pollination, self hand-pollination, natural selfing and apomixis are presented in **Figure 1** (see appendix 1 for table with values). Heterospecific pollen reduced seet set significatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05.

@@

>>>>

Add effect sizes to analysis!!

@@

Results of hand cross-pollination, self hand-pollination, natural selfing and apomixis are presented in **Figure 1** (see appendix 1 for table with values). Heterospecific pollen reduced seet set significatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05. Moreover, effect sizes differ across species, see **Figure 2** where species like *S. lycopersicum* had a large effect size and other's like *E. sativa* a small or null effect size.

@@

Maybe for this plot I have to do hedges'g instead of cohean because of different sample sizes when I group the treatments per family. Check
